Partridge: An effective system for the automatic classification of the types of academic papers

### 2013-05-22 doc/bcspaper/article.tex
Added coresc pie charts for review and research papers

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{svmult}
%
%% choose options for [] as required from the list
%% in the Reference Guide
%
\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                             % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%
%% see the list of further useful packages
%% in the Reference Guide
%
%\makeindex             % used for the subject index
%                       % please use the style svind.ist with
%                       % your makeindex program
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{document}

@@

%\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

%\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.\newline\indent
%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

\section{Introduction}
\label{sec:1}
Since the advent of the `Digital Age' and the ability of computers to copy and reproduce information for a negligible cost, the amount of information available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million papers were published in the year 2006 alone\cite{bjork2009}.
As available information increases, relevant material becomes progressively more difficult to find manually and the need for an automated information retrieval tool more apparent.
There are already a large number of information retrieval and recommendation systems for scientific publications.  Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso (\url{http://www.textpresso.org/}) index only publications from predefined journals or topics (for the above examples, Agriculture, Biology and Bioinformatics respectively).
Unfortunately, these domain specific indexing systems usually only contain a small subset of papers, excluding potentially crucial literature because it does not quite fit into the subject domain. 
%This problem is often exacerbated by the decision to leave out some papers and articles because the system administrators do not have permission from the author or publisher to include them. 
The value of these systems to their users is often restricted by the small proportion of available literature that they index, forcing researchers to use multiple, domain specific, search engines for their queries.
In contrast, there are also a number of interdisciplinary indexing systems and online journals such as arXiv( \url{http://arxiv.org/}), PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers from as many disciplines as possible. The traits of these systems often complement those of their domain-specific counterparts; they provide a comprehensive collection of literature but insufficient filtering and indexing capabilities.
One of the most publicised and well known interdisciplinery scientific literature search systems is Google Scholar (\url{http://scholar.google.com}). Google offers advanced query options specific to Scholar that allow searching by author, year and for words that occur only in the document title.

@@

%how papers were acquired 
The papers were downloaded from PLoS using XXX (bookmarklet? plosget.py using the PLoS restful search API? choosing first N available? or by keyword?)
The number of papers downloaded per paper type category was as follows: 200 Essay, 99 Correspondence, 174 Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
These formed a corpus of 1352 papers.

@@

\begin{figure}[t]
\sidecaption[t]
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the option graphics use
%\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
\caption{coresc pies}
%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
\label{fig:coresc_pies} 
\end{figure}

>>>>

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{svmult}
%
%% choose options for [] as required from the list
%% in the Reference Guide
%
\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                             % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{subcaption}
\captionsetup{compatibility=false}
%
%% see the list of further useful packages
%% in the Reference Guide
%
%\makeindex             % used for the subject index
%                       % please use the style svind.ist with
%                       % your makeindex program
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{document}

@@

\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
the ability of computers to copy and reproduce information for a negligible
cost, the amount of information available to researchers has been increasing
drastically.  B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
papers were published in the year 2006 alone\cite{bjork2009}.  As available
information increases, relevant material becomes progressively more difficult
to find manually and the need for an automated information retrieval tool more
apparent.  There are already a large number of information retrieval and
recommendation systems for scientific publications.  Many of these systems,
such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane
Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
(\url{http://www.textpresso.org/}) index only publications from predefined
journals or topics (for the above examples, Agriculture, Biology and
Bioinformatics respectively).  Unfortunately, these domain specific indexing
systems usually only contain a small subset of papers, excluding potentially
crucial literature because it does not quite fit into the subject domain. 
%This problem is often exacerbated by the decision to leave out some papers and
%articles because the system administrators do not have permission from the
%author or publisher to include them. 
The value of these systems to their users is often restricted by the small
proportion of available literature that they index, forcing researchers to use
multiple, domain specific, search engines for their queries.  In contrast,
there are also a number of interdisciplinary indexing systems and online
journals such as arXiv( \url{http://arxiv.org/}),
PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
that try to incorporate wide ranges of papers from as many disciplines as
possible. The traits of these systems often complement those of their
domain-specific counterparts; they provide a comprehensive collection of
literature but insufficient filtering and indexing capabilities.  One of the
most publicised and well known interdisciplinery scientific literature search
systems is Google Scholar (\url{http://scholar.google.com}). Google offers
advanced query options specific to Scholar that allow searching by author, year
and for words that occur only in the document title.

@@

%how papers were acquired 
The papers were downloaded from PLoS using {\em plosget.py}, a short python
script that uses the PLoS restful search API. The number of papers downloaded
per paper type category was as follows: 200 Essay, 99 Correspondence, 174
Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107, Case Study, 312
Review, 200 Research.  These formed a corpus of 1459 papers.

@@

\begin{figure}[t]
\sidecaption[t]
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the option graphics use
%\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
\centering
%\begin{subfigure}[b]{0.6\textwidth}
\includegraphics[width=\textwidth]{figures/review_corescs.png}
%\caption{CoreSC content for a sample review paper}
%\end{subfigure}
%\begin{subfigure}[b]{0.6\textwidth}
\includegraphics[width=\textwidth]{figures/report_corescs.png}
%\caption{CoreSC content for a sample research paper}
%\end{subfigure}
\caption{coresc pies}
%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
\label{fig:coresc_pies} 
\end{figure}
